% LaTeX snippets for insertion into the report
% Paste sections where appropriate in your main .tex file

% --- Build and Run Instructions ---
\subsection*{Build and Run (Test Instructions)}
To build the simulator:
\begin{verbatim}
make
\end{verbatim}

To compile and run the provided test assembly files (uses `./gcc.py` to produce riscv `.elf` files):
\begin{verbatim}
cd tests
./build_and_run_tests.sh
\end{verbatim}

The script compiles each `.s` file to an `.elf` using `./gcc.py` and then runs `./sim` with summary logging. Output logs are written to `tests/build/*.log`.

% --- Table template for predictor results ---
\begin{table}[h!]
\centering
\caption{Branch prediction results for \texttt{<program>}}
\begin{tabular}{lrrrr}
\hline
Predictor & Size & Predictions & Mispredictions & Accuracy (\%) \\
\hline
NT        & -    & 0      & 0          & 0.00 \\
BTFNT     & -    & 0      & 0          & 0.00 \\
Bimodal   & 256  & 0      & 0          & 0.00 \\
Bimodal   & 1024 & 0      & 0          & 0.00 \\
Bimodal   & 4096 & 0      & 0          & 0.00 \\
Bimodal   & 16384& 0      & 0          & 0.00 \\
gShare    & 256  & 0      & 0          & 0.00 \\
gShare    & 1024 & 0      & 0          & 0.00 \\
gShare    & 4096 & 0      & 0          & 0.00 \\
gShare    & 16384& 0      & 0          & 0.00 \\
\hline
\end{tabular}
\end{table}

% --- Test program descriptions (appendix) ---
\subsection*{Appendix: Test Programs}
\begin{itemize}
  \item \textbf{r\_tests.s}: Exercises R-type instructions (add, sub, and, or, xor, shifts, slt/sl tu).
  \item \textbf{i\_tests.s}: Exercises I-type instructions (addi, andi, ori, xori, slti, slli, srli, srai).
  \item \textbf{mem\_branch\_tests.s}: Exercises memory (sw, lw) and a small loop to test branches.
  \item \textbf{m\_tests.s}: Exercises M-extension instructions (mul, mulh, mulhu, div, divu, rem, remu).
  \item \textbf{syscall\_tests.s}: Tests `ecall` handling for getchar and putchar.
\end{itemize}

% --- What to collect and paste here ---
Please attach the following into the appendix when you run the tests and pass results back:
\begin{itemize}
  \item One log file per test from `tests/build/*.log` (or a subset you find interesting).
  \item The branch prediction summary printed to stdout by the simulator for each test (copy-paste into the Results section).
  \item Any mismatches you observed between expected register/memory values and simulator results.
\end{itemize}
